Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-04 Latex Source/paper.tex
add music credits for songs w/lyrics and update gitignore

% \begin{figure}
%   \includegraphics[width=0.3\textwidth]{typing_test_1}
%   \caption{Starting window of typing test}
%   \Description{Image of the starting windows of the typing test}
% \end{figure}

% \begin{figure}
%   \includegraphics[width=0.3\textwidth]{typing_test_2}
%   \caption{Test started}
%   \Description{Image of the test with the lyrics that the user will type}
% \end{figure}

% \begin{figure}
%   \includegraphics[width=0.3\textwidth]{typing_test_3}
%   \caption{Test finished}
%   \Description{Image of the finished test}
% \end{figure}

\begin{figure}
  \includegraphics[width=\textwidth]{typingTest}
  \caption{Typing Test Screenshots}
  \Description{Images of what the user will see in the typing test}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.3\textwidth]{eyetracker_setup.png}
  \caption{EyeWriter 2.0}
  \Description{Image of the eye tracker setup}
\end{figure}

During the cognitive task component of the study, participants performed a Quantified Behavioral test or QBTest while their eye movements were tracked by the EyeWriter 2.0.
The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

@@

\subsection[short]{Participants and Design}
Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

@@

\section{Conclusion}
Conclusion

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{typingTest}
  \caption{Images of what the user will see in the typing test}
  \Description{Images of what the user will see in the typing test}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{eyetracker_setup.png}
  \caption{EyeWriter 2.0 Setup}
  \Description{Image of the eye tracker setup}
\end{figure}

During the cognitive task component of the study, participants performed a Quantified Behavioral test or QBTest while their eye movements were tracked by the EyeWriter 2.0.
The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.

\begin{figure}
  \includegraphics[width=\textwidth]{qbTest.png}
  \caption{Images of what the user will see in the QBTest}
  \Description{Images of what the user will see in the QBTest}
\end{figure}

% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

@@

\subsection[short]{Participants and Design}
Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. Two males and eight females all in the age range of 18-23. There were no restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

@@

\section{Conclusion and Future Works}
Conclusion
